Principally, pressures arising from economic activity can either be tallied at
the actual place of production or at the point of the consumption.
Traditionally, the accounting at the actual place of production has been used
for policy decisions. For example, the Kyoto Protocol was based on the
production principle, which is now discussed to be one of the reasons for its
limited success [[HELM 2012 climate policy]]. 

Consumption based accounting (CBA), on the other hand, just recently gained
momentum for policy making [[harris symons]]. In CBA, all resource use and environmental
pressurs (for example emissions) occurring along the the supply chain of
products are added up and allocated to the final consumer of the product. This
allows for example to assess the environmental pressure caused by a domestic
demand abroad [[weinzettel, caldera, ]]

Indicators based on consumption based accounting are also known as various
types of 'footprints' and are increasingly used for informing policy makers as
well as the public about ongoing environmental (Arnold Tukker et al. 2014;
Steen-Olsen et al. 2012; Kanemoto et al. 2013; United Nations University and
International Human Dimensions Programme on Global Environmental Change 2012)
and social problems (Simas et al. 2014). 

CBA requires a comprehensive description of the global socio-economic
metabolism including among other the structure of domestic economies, their
ressource use and the amount of trade between countries and regions.
Environmentally Extended Multi Regional Input-Output databases (EEMRIO) provide
all these data in a consistent framework. Compiling an EE MRIO database is a
data intensive task, and only a handful of these databases are available today
[[TUKKER DIETZ]]. These databases differ in their environmental and regional
focus and also due to the applied accounting principles and implementation
details [[row paper, dan paper, kjartan comaprison]]. 